MLH1 Data Report

### 2019-12-31 doc/Main_Report_Results.rmd
forgot what updates were

A general pattern is that the female data has higher within mouse variance (both var and cV). I think the dissection date needs to be tested as a predictor factor.  It might be tricky to add the dissection date metric. 
Test if dissection date is more significant predictor than strain (for females)

@@

>>>>

A general pattern is that the female data has higher within mouse variance (both var and cV). Some strains more than others. I think the dissection date needs to be tested as a predictor factor.  It might be tricky to add the dissection date metric. 
Test if dissection date is more significant predictor than strain (for females)
Also test how the number of 0CO bivalents per cell affects mouse with variance.

@@

I don't have enough mice with >15 cells for a complete idea of the distributions, but comparing single mice with enough good quality cells show be
